MSc Thesis

### 2023-03-19 manuscript/main.tex
created summary statistics

To answer test all three of our hypotheses, I used linear mixed effects models implemented in (\cite{douglas_bates_2023_7529836}) in Julia 1.8.5 (\cite{bezanson2017julia}). Prior to running our full model, I first tested for an effect of biomass of silicon content, as in other defensive pathways plant size shows corelations with defense levels \cite{carmona_plant_2011}. We found a negative correlation between plant size and silicon content ($\beta = -0.067 \pm 0.017, p < 0.001$), and thus included plant size as a covariate in our final model. Thus, we tested the effects of our species and induction treatments on measured leaf silicon using the following model formula:

\[Si ~ Species * Induction + Biomass + (1|Genotype)\]
%[Insert text about how great these models are]. I specified a hierarchical model using the following model:

@@

Among our cultivars, silicon content ranged from [x]\% to [y]\% of dry mass. [Species a] had the highest amount of silicon at [z]\%, while [species b] had the lowest silicon content at [z]\%. Overall, methyl-jasmonate and insect treatments increased plant silicon by [x] and [y]\% respectively. Our model showed that both species and treatment type had effects on the plant silicon content. Parameter estimates and 90\% credible intervals are summarized in Table \ref{Tab:params}. Species and induction treatments had an interaction.

>>>>

To test all three of our hypotheses, I used linear mixed effects models implemented in (\cite{douglas_bates_2023_7529836}) in Julia 1.8.5 (\cite{bezanson2017julia}). Prior to running our full model, I first tested for an effect of biomass of silicon content, as in other defensive pathways plant size shows corelations with defense levels \cite{carmona_plant_2011}. We found a negative correlation between plant size and silicon content ($\beta = -0.067 \pm 0.017, p < 0.001$), and thus included plant size as a covariate in our final model. Thus, we tested the effects of our species and induction treatments on measured leaf silicon using the following model formula:

\[Si \sim Species * Induction + Biomass + (1|Genotype)\]
%[Insert text about how great these models are]. I specified a hierarchical model using the following model:

@@

\subsection{Results}
Oats had the lowest silicon content at 0.34\%. Overall, methyl-jasmonate and insect treatments increased plant silicon by [x] and [y]\% respectively. Our model showed that both species and treatment type had effects on the plant silicon content. Parameter estimates and 90\% credible intervals are summarized in Table \ref{Tab:params}. Species and induction treatments had an interaction.
